---
title: "Bike Sharing"
author: "Sahil kumar"
date: "February 18, 2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

<b>
Title   : Analysis of Bike Sharing Dataset<br>
Name    : Sahil kumar<br>
Email   : sahilriders@gmail.com<br>
College : Institute of Engineering and Management , Kolkata<br>
</b>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Setting Working Directory
```{r}
setwd("G:/Intern - IIM Lucknow/Bike-Sharing-Dataset")
```
#Loading necessary packages
```{r}
library(psych)
library(car)
library(corrgram)
library(ggplot2)
library("lattice", lib.loc="C:/Program Files/R/R-3.4.3/library")
```

#Reading Dataset
```{r}
df <- read.csv(paste("hour.csv",sep=""))
View(df)
```

#Describing Dataset
```{r}
describe(df)
```

```{r}
str(df)
```

*There are two types of customers :-
 1. Casual
 2. Registered
 
*Last 3 columns represents bike sharing among casual, registered and both customers.

# EDA

# Season vs Bike Shared
<b>TABLE</b>
```{r}
attach(df)
aggregate(cbind(casual,registered,cnt)~season,data=df,mean)
```

<b>BOXPLOTS</b>
```{r}
par(mfrow=c(3,1))
bwplot(season~casual ,data=df,xlab = "Total count of bike sharing",main='Casual Customers')
bwplot(season~registered ,data=df,xlab = "Total count of bike sharing",main='Registered Customers')
bwplot(season~cnt ,data=df,xlab = "Total count of bike sharing",main='All customers')
```

<b>Inference :</b>
<ol>
<li> Maximum bike sharing is done in Season 3.</li>
<li>2. Bike shared among registered users is more than casual users.</li>
</ol>

# Month vs Bike shared

<b>TABLE</b>
```{r}
aggregate(cbind(casual,registered,cnt)~mnth,data=df,mean)
```

<b>BOXPLOTS</b>
```{r}
par(mfrow=c(3,1))
plot(aggregate(casual~mnth ,data=df,mean),xlab='Month',ylab='Count of Bike shared',main='casual users')
plot(aggregate(registered~mnth ,data=df,mean),xlab='Month',ylab='Count of Bike shared',main='registered users')
plot(aggregate(cnt~mnth ,data=df,mean),xlab='Month',ylab='Count of Bike shared',main='all users')
```

<b>Inference:-</b><br>
On an Average , most bike sharing happens between March to November month.
<br>
<b>Hypothesis:-</b><br>
Reason of low bike sharing in other months can be LOW TEMPERATURE.

# Hour vs Bike shared

<b>TABLE</b>
```{r}
aggregate(cbind(casual,registered,cnt)~hr,data=df,mean)
```

<b>BOXPLOTS</b>
```{r}
par(mfrow=c(3,1))
plot(aggregate(casual~hr ,data=df,mean),xlab='Hour of the day',ylab='Count of Bike shared',main='casual users')
plot(aggregate(registered~hr ,data=df,mean),xlab='Hour of the day',ylab='Count of Bike shared',main='registered users')
plot(aggregate(cnt~hr ,data=df,mean),xlab='Hour of the day',ylab='Count of Bike shared',main='all users')
```

<b>Inference :-</b><br>
1. For casual customers , bike sharing starts around 7am ,reaches its peak around 2pm then further decreases.<br>
2. In General , bike sharing reaches its peak around 8 am ,declines and again rises to reach its peak around 5pm.<br>

<b>Hypothesis:</b><br>
Bike sharing is more in morning and evening.<br>
Not in afternoon , maybe due to excess heat.<br>

# EFFECT OF HOLIDAYS ON BIKE SHARING

<b>TABLE</b>
```{r}
mytable<-aggregate(cbind(casual,registered,cnt)~holiday ,data=df,mean)
mytable

```

<b>BARCHARTS</b>
```{r}
par(mfrow=c(1,3))
barchart(casual~holiday,data=mytable,horizontal=FALSE,ylim=c(0,50))
barchart(registered~holiday,data=mytable,horizontal=FALSE,ylim=c(0,200))
barchart(cnt~holiday,data=mytable,horizontal=FALSE,ylim=c(0,200))
```

# EFFECT OF WEATHER SITUATION ON TOTAL BIKE SHARING

<b>TABLE</b>
```{r}
wsittable<-aggregate(cnt~weathersit ,data=df,mean)
wsittable
```

<b>BOXPLOTS</b>
```{r}
bwplot(weathersit~cnt,data=df,xlab ="No of total bike shared",ylab="Different weather situation",main="")
```
Weather Situtation 1 is highly suitable for bike sharing.

# Scatterplot of temp vs total bike sharing
```{r}
histogram(df$temp)
scatterplot(cnt~temp,data=df)
```

#Humidity
```{r}
histogram(df$hum)
scatterplot(cnt~hum,data=df)
```

#Windspeed
```{r}
histogram(df$windspeed)
scatterplot(cnt~windspeed,data=df)
```

#Correlation Analysis

```{r}
corrgram(df,lower.panel=panel.shade,
         upper.panel=panel.pie, text.panel=panel.txt,
         main="Corrgram")
```

```{r}
df_subset <- df[,10:17]


df_cor <- cor(df_subset)
library(corrplot)
corrplot(df_cor, method = 'color', addCoef.col="black")
```

#T-TEST
```{r}
t.test(cnt~holiday,data=df)
```

<b>It means that there is significance difference in bike sharing if the day is holiday or not</b>

#Regression Analysis

We are going to fit 'cnt' which is count of bike shared wrt to the factors: weathersit,temp,atemp,hum,windspeed,casual,registered.
<br>
In order to test this hypothesis, we are proposing this model:
<br>
y=b0 + b1\*weathersit + b2\*temp + b3\*atemp + b4\*hum + b5\*windspeed + b6\*casual + b7\*registered

```{r}
mod1 <-lm(cnt~weathersit+temp+atemp+hum+windspeed+casual+registered,df)
summary(mod1)
```

**Inference :**
We can see that the Residual standard error is very low which means that overall the model is a good fit.<br>
p-value corresponding to each variable is also less than 0.5 which means that they are significant for the model. <br>
Most significant variables are Weathersit, temp, windspeed, casual and registered. <br>
F-statistic is also very high which means tht our hypothesis is compatible with the observed data. <br>

