---
title: "Airline Pricing"
author: "Sahil kumar"
date: "February 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Reading the dataset
```{r}
airline<-read.csv(paste("SixAirlinesDataV2.csv",sep=""))
View(airline)
```

#Summary
```{r}
library(psych)
describe(airline)
```

```{r}
str(airline)
```

#Mean
```{r}
apply(airline[,6:18], MARGIN =2, FUN=mean)
```

#Median
```{r}
apply(airline[,6:18], MARGIN =2, FUN=median)
```

#Standard Deviation
```{r}
apply(airline[,6:18], MARGIN =2, FUN=sd)
```

#Visualisation

```{r}
#Airline Speifications

par(mfcol=c(1,2))
pie(table(airline[,"Airline"]),col=c("blue","Red","green","pink","yellow","black"),main="Airline Distribution")
pie(table(airline[,"Aircraft"]),col=c("red","blue"),main="Aircraft Manufacturer")
```

```{r}
par(mfrow=c(1,2))
hist(airline[,"FlightDuration"], xlab = "Flight Duration(hrs)", ylab = "Frequency", main="Flight duration histogram", col=c("red", "green","yellow"), xlim = c(0,16), ylim = c(0, 60))

boxplot(airline[,"FlightDuration"], xlab = "Flight Duration(hrs)", ylab = "Frequency", main = "Flight Duration boxplot")

```

```{r}
par(mfrow=c(1,2))
hist(airline[,"SeatsEconomy"], xlab = "Number of Economy seats", ylab = "Frequency", main="seat economy histogram", col=c("red", "green"), xlim = c(0,500), ylim = c(0, 200))

boxplot(airline[,"SeatsEconomy"], xlab = "Number of Economy seats", ylab = "Frequency", main = "Seat econnomy boxplot")
```

```{r}
par(mfrow=c(1,2))
hist(airline[,"SeatsPremium"], xlab = "Number of Premium seats", ylab = "Frequency", main="seat premium histogram", col=c("red", "green"), xlim = c(0,70), ylim = c(0, 200))

boxplot(airline[,"SeatsPremium"], xlab = "Number of Premium seats", ylab = "Frequency", main = "Seat premium boxplot")

```

```{r}
pie(table(airline[,"TravelMonth"]),col=c("blue", "green", "red", "yellow", "orange", "purple"), main="Common Travel Month")
```

#Economy Seats
```{r}
library(car)

scatterplot(airline$SeatsEconomy, airline$PriceEconomy, main="Price of Economy seats vs. no of Economy seats ", xlab = "seats", ylab = "price")
```

#Premium Economy
```{r}
scatterplot(airline$SeatsPremium, airline$PricePremium, main="Price of Economy seats vs. no of Economy seats ", xlab = "seats", ylab = "price")
```

```{r}
library(lattice)
histogram(~PriceEconomy | IsInternational, data=airline, col="blue", main = "Price of economy class tickets in international and domestic flights")
```

```{r}
boxplot(airline$PriceEconomy~airline$IsInternational, ylab= "Price Economy", xlab="Flight type", col=c("blue","red"), main="Price of economy class tickits in interantional and domestics flights")
```

#Price wrt Flight Duration
```{r}
par(mfrow=c(2,1))
scatterplot(airline$PricePremium,airline$FlightDuration,main="premium class pricing with flight duration")
scatterplot(airline$PriceEconomy,airline$FlightDuration,main="economy class pricing with flight duration")
```

#Pitch Difference
```{r}
barchart(PitchDifference ~ Airline, data=airline, groups=IsInternational, auto.key=TRUE, par.settings = simpleTheme(col=c("white", "black")), main="ptich difference in each airline with terminal", xlab="airlines")
```

#Width Difference
```{r}
barchart(WidthDifference ~ Airline, data=airline, groups=IsInternational, auto.key=TRUE, par.settings = simpleTheme(col=c("white", "black")), main="Width difference in each airline with terminal", xlab="airlines")
```

#Corrgram
```{r}
library(corrgram)
corrgram(airline,order=TRUE,lower.panel=panel.shade,upper.panel = panel.pie,main="Corrgram")
```

#T-Test
Null Hypothesis : There is no difference between price of Economy and Premium Economy class

Alternate Hypothesis : Price of premium economy class is higher than the price of economy class
```{r}
t.test(airline$PriceEconomy,airline$PricePremium)
```

As p-value<0.05 , so null hypothesis is rejected .

#Pearson's Correlation Test

1. Between difference in price vs width difference
```{r}
cor.test((airline$PricePremium-airline$PriceEconomy),airline$WidthDifference)
```

2. Between difference in price vs pitch difference
```{r}
cor.test((airline$PricePremium-airline$PriceEconomy),airline$PitchDifference)
```
p-value >0.05 . Not significant

3.Between difference in price vs fight duration
```{r}
cor.test((airline$PricePremium-airline$PriceEconomy),airline$FlightDuration)
```

#Regression Analysis
```{r}
fit <- lm((airline$PricePremium-airline$PriceEconomy)~airline$PitchDifference+airline$WidthDifference+airline$FlightDuration)

summary(fit)
```
```{r}
fit$coefficients
```

From the regression analysis , we can conclude that
* Flight Duration plays an important part in deciding the price difference
* Widht Difference is also important.
* In case of pitch difference , p-value = 0.6174>0.05 , thus it is not significant.

Overall , p-value <0.05 for the model , so we can say that it is a good model.
