---
title: "MBA Starting Salaries"
author: "Sahil kumar"
date: "February 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Reading Dataset
```{r}
mba <- read.csv(paste("MBA Starting Salaries Data.csv",sep=""))
View(mba)
```

#Describing Dataset
```{r}
library(psych)
describe(mba)
```

#Visualization Plots
```{r}
mba$sex=factor(mba$sex, levels=c(1,2), labels=c("Male","Female"))
plot(mba$sex,col = "red",main = "Gender distribution in MBA Schools")
```

```{r}
hist(mba$gmat_tot, xlab="GMAT total score",main="GMAT scores of Students", breaks=15,col="blue")
```

```{r}
hist(mba$work_yrs,col="red",xlab="years of work experience",main = "Work Experience",breaks = 10)
```

```{r}
boxplot(mba$salary, main="Salary Details",
              col=c("red"),horizontal=TRUE,
              xlab="Salary" )
```

```{r}
fl= factor(mba$frstlang, levels=c(1,2), labels=c("English","Others"))
    plot(fl,col="yellow",main = "Language Distribution")
```

```{r}
f1<- mba[ which(mba$satis<='7'), ]
hist(f1$satis,breaks =5,col="green",xlab="Degree of Satisfaction (1=low,7=high)", main="Satisfaction  distribution of MBA students")
```

#Creating Subset for those who got a job
```{r}
jobmba<-subset(mba,salary!=0)
jobmba1<-subset(jobmba,salary!=999)
jobf<-subset(jobmba1,salary!=998)

summary(jobf)[,c(1:5,12)]
```


#Comparison of salary wrt different features
```{r}
library(car)    
scatterplot(salary ~ age,data=jobf,
            main="Scatter plot of salary vs age",
            xlab="age",
            ylab="salary")
```

```{r}
scatterplot(salary ~gmat_tot,data=jobf,
            spread=FALSE, smoother.args=list(lty=2),
            main="Scatter plot of salary vs Gmat total",
            xlab="Gmat score",
            ylab="salary")
```

```{r}
library(lattice)

mba$frstlang=factor(mba$frstlang,levels=c(1,2),labels=c("English","Others"))
bwplot(frstlang ~salary,data=jobf,horizontal="TRUE",ylab="language spoken (1=english,2=rest)")
```

```{r}
bwplot(sex ~ salary, data=mba, horizontal=TRUE, 
       xlab = "Salary")
```

```{r}
bwplot(satis~salary,jobf,xlab="Salary")
```

```{r}
bwplot(work_yrs~salary,jobf)
```

#Comparing Factors
```{r}
bwplot(work_yrs ~ salary | sex, data=mba, 
       horizontal=TRUE, xlab="Income")
```
```{r}
bwplot(quarter ~ salary | sex, data=mba, 
       horizontal=TRUE, xlab="Income")

```

#Corrgram Visualization
```{r}
library(corrgram)
corrgram(mba,lower.panel=panel.shade,
         upper.panel=panel.pie, text.panel=panel.txt,
         main="Corrgram of salary intercorrelations")
```

#Correlation Matrix
```{r}
x <- jobf[,c("age", "gmat_tot", "gmat_qpc", "gmat_vpc","gmat_tpc","s_avg","f_avg","work_yrs","salary")]
cor(x,x)
```

#Few contigency tables 

#1. Sex vs Salary
```{r}
mytable<-xtabs(~salary+sex,jobf)
   mytable
```

#Chi Square Test
```{r}
chisq.test(mytable)
```

#t-Test
```{r}
t.test(salary ~ sex, data=jobf)
```

Inference:
Men are paid more than Females.

#2. Effect of First Language on Salary
```{r}
 mytable1<-xtabs(~salary+frstlang,jobf)
   mytable1
```

```{r}
chisq.test(mytable1)
```

```{r}
 t.test(salary ~ frstlang, data=jobf)
```

#3. Effect of Work Years on Salary
```{r}
mytable2<-xtabs(~salary+work_yrs,jobf)
   mytable2
```

```{r}
chisq.test(mytable2)
```
Thus There is a relation between Work experience and Placement Salaries;2 years is optimal.

#Regression Analysis

#Analysis 1
```{r}
m1<-lm(salary~quarter+s_avg+f_avg+age,jobf)
summary(m1)
```

Age is only significant variable here.

#Analysis 2
```{r}
m2<-lm(salary~gmat_tot+gmat_tpc+gmat_vpc+gmat_qpc,jobf)
summary(m2)
```
gmat_tpc is a significant variable.

#Analysis 3
```{r}
m3<-lm(salary~sex+frstlang+satis+work_yrs+quarter,jobf)
summary(m3)
```
Work years and FirstLang are important variables.

# People who didn't got any job
```{r}
nojob<-subset(mba,salary==0)

summary(nojob)
```
```{r}
hist(nojob$satis, xlab="Satisfaction",main="MBA Satisfaction", breaks=7,col="blue")
```


