---
title: "Dean's Dilemma (Part-II)"
author: "Sahil kumar"
date: "February 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reading file
```{r}
df <- read.csv("Data - Deans Dilemma.csv")
View(df)
```
# Dataframe for placed
```{r}
placed <- df[which(df$Placement=="Placed"),]
View(placed)
```


# R code that creates a table showing the mean salary of males and females, who were placed.
```{r}
mytable <- aggregate(placed$Salary ,by=list(placed$Gender),mean)
mytable
```
Average Salary of males are higher than the females.

Average salary of male = 284241.9
Average salary of female = 253068.0

#Use R to run a t-test to test the following hypothesis:
  H1: The average salary of the male MBAs is higher than the average salary of female MBAs.
```{r}
t.test(Salary~Gender ,data=placed)
```

p-value is 0.00234

As p-value < 0.05 . So ,Null hypothesis is rejected that difference in mean salary of M & F is 0.
Thus, The average salary of the male MBAs is higher than the average salary of female MBAs.
