---
title: "Dean's Dilemma"
author: "Sahil kumar"
date: "February 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(psych)
library(lattice)
library(car)
```


# Reading File
```{r}
setwd("G:\\Intern - IIM Lucknow")
df <- read.csv("Data - Deans Dilemma.csv")
View(df)
```

# Describing Dataset
```{r}
describe(df)
```

# Use R to calculate the median salary of all the students in the data sample
```{r}
median(df$Salary)
```

# Use R to calculate the percentage of students who were placed, correct to 2 decimal places.
```{r}
options(digits=4)
mytable=prop.table(table(df$Placement))*100
mytable[2]
```

# Use R to create a dataframe called placed, that contains a subset of only those students who were successfully placed.
```{r}
placed=df[which(df$Placement=='Placed'),]
View(placed)
```

# Use R to find the  median salary of students who were placed.
```{r}
median(placed$Salary)
```

# Use R to create a table showing the mean salary of males and females, who were placed. 
```{r}
mytable <- aggregate(Salary~Gender ,data=placed,mean)
mytable
```

# Use R to generate a histogram showing breakup of the MBA performance of the students who were placed
```{r}
hist(placed$Percent_MBA ,main="MBA Performance of placed students",
          xlab="MBA Percentage",ylab="Count",
          xlim=c(50,80),ylim=c(0,150),breaks=3,col="grey")
```

# Create a dataframe called notplaced, that contains a subset of only those students who were NOT placed after their MBA.
```{r}
not_placed=df[which(df$Placement=='Not Placed'),]
View(not_placed)
```

# Draw two histograms side-by-side, visually comparing the MBA performance of Placed and Not Placed students
```{r}
par(mfrow=c(1,2))

hist(placed$Percent_MBA ,main="MBA Performance of placed students",
          xlab="MBA Percentage",ylab="Count",
          xlim=c(50,80),ylim=c(0,150),breaks=3,col="grey")

hist(not_placed$Percent_MBA ,main="MBA Performance ofnot placed students",
          xlab="MBA Percentage",ylab="Count",
          xlim=c(50,80),ylim=c(0,50),breaks=3,col="grey")

```

# Use R to draw two boxplots, one below the other, comparing the distribution of salaries of males and females who were placed
```{r}
bwplot(placed$Gender~placed$Salary ,data=placed,xlab="Salary",ylab="Gender",main = "Comparison of Salaries of Males and Females")
```

# Create a dataframe called placedET, representing students who were placed after the MBA and who also gave some MBA entrance test before admission into the MBA program. 
```{r}
placedET <- placed[which(placed$S.TEST==1),]
View(placedET)
```
# Draw a Scatter Plot Matrix for 3 variables -- {Salary, Percent_MBA, Percentile_ET} using the dataframe placedET.
```{r}
scatterplotMatrix(formula= ~Salary+Percent_MBA+Percentile_ET ,data=placedET)
```

