---
title: "Titanic"
author: "Sahil kumar"
date: "February 2, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 2b : Reading the dataset

```{r titanic}
titanic <- read.csv("Titanic Data.csv")
head(titanic)
```

# Task 3a : Use R to count the total number of passengers on board the Titanic.
```{r}
nrow(titanic)
```
There were 889 passengers on board the Titanic.

# Task 3b : Use R to count the number of passengers who survived the sinking of the Titanic.
```{r}
mytable <- with(titanic,table(Survived))
addmargins(mytable)
```
Thus, Out of 889 passengers only 340 could survive.

# Task 3c : Use R to measure the percentage of passengers who survived the sinking of the Titanic.
```{r}
prop.table(mytable)*100
```
Only 38.24522% passengers could survive.

# Task 3d : Use R to count the number of first-class passengers who survived the sinking of the Titanic.
```{r}
mytable2 <- xtabs(~Survived+Pclass , data=titanic)
addmargins(mytable2)
```
134 out of 214 first class passengers survived.

# Task 3e : Use R to measure the percentage of first-class passengers who survived the sinking of the Titanic.
```{r}
prop.table(mytable2,2)*100
```
62.61682% of First Class Passenger survived.

# Task 3f : Use R to count the number of females from First-Class who survived the sinking of the Titanic
```{r}
mytable3 <- xtabs(~Pclass+Sex+Survived , data=titanic)
mytable3
```
89 females from First-Class survived the sinking of the Titanic

# Task 3g : Use R to measure the percentage of survivors who were female
```{r}
mytable4 <- xtabs(~Sex+Survived , data=titanic)
prop.table(mytable4,2)*100
```
67.94118% of survivors were female.

# Task 3h : Use R to measure the percentage of females on board the Titanic who survived
```{r}
prop.table(mytable4,1)*100
```
74.03846% of females on board the Titanic survived.

# Task 3i : Run a Pearson's Chi-squared test to test the following hypothesis:

Hypothesis:  The proportion of females onboard who survived the sinking of the Titanic was higher than the proportion of males onboard who survived the sinking of the Titanic.
```{r}
chisq.test(mytable4)
```
The p-values are the probability of obtaining the sampled results, assuming independence of the row and column variables in the population. Since the probability is small (p < 0.01), we reject the Null hypothesis that survival of passenger and sex of passenger are independent.

Thus it suggests that whether a passenger will survive or not, depends on the sex of the passenger(male or female).
